How environmental drivers of spatial synchrony interact

### 2021-07-29 Paper/SupMat.Rnw
mostly small changes

If $w=(w_1,\ldots,w_N)$ is a stationary stochastic process, where the index $i=1,\ldots,N$ corresponds
to sampling locations, then we measure the synchrony of $w$ as 
\begin{equation}
\rho_{ww} = \left( \frac{1}{N^2-N}  \right) \sum_{i \neq j} S_{w_i w_j},
\end{equation}
where $S_{ww}$ is the spectral matrix of the process $w$. This is a function of frequency or timescale.
To see that $\rho_{ww}$ is a real-valued function, note that $\conj{S_{ww}}=S_{ww}^\tau$, where the superscript 
$\tau$ denotes matrix transpose (REF to Brillinger theorem 2.5.1 on p. 24).
%***DAN: Don't forget to fill in this reference!
Therefore 
\begin{align}
\conj{\rho_{ww}} &= \left( \frac{1}{N^2-N}  \right) \sum_{i \neq j} \conj{S_{w_i w_j}} \\
&= \left( \frac{1}{N^2-N}  \right) \sum_{i \neq j} S_{w_j w_i} \\
&= \left( \frac{1}{N^2-N}  \right) \sum_{i \neq j} S_{w_i w_j} \\
&= \rho_{ww}.
\end{align} 
The quantity $\rho_{ww}$ makes sense as a measure of synchrony in part because 
\begin{align}
\rho_{ww} &= \Rp(\rho_{ww}) \\
&= \left( \frac{1}{N^2-N} \right) \sum_{i \neq j} \Rp(S_{w_i w_j}).
\end{align}
The quantity $\Rp(S_{w_i w_j})$ is the cospectrum of the component processes $w_i$ and $w_j$, 
and an appropriate integral across frequencies of the cospectrum equals the covariance, 
$\cov(w_i,w_j)$ (REF to some specific page/theorem in Brillinger). 
%***DAN: Don't forget to add
Thus an integral of $\rho_{ww}$ across frequencies equals 
\begin{equation}
\left( \frac{1}{N^2-N} \right) \sum_{i \neq j} \cov(w_i,w_j),
\end{equation}
which is a standard quantity that can be used to measure non-frequency-specific synchrony.
Thus $\rho_{ww}$ is a frequency-specific generalization of a classic, non-frequency-specific 
measure of synchrony.

If $\epsilon^{(1)}=(\epsilon^{(1)}_1,\ldots,\epsilon^{(1)}_N)$ and 
$\epsilon^{(2)}=(\epsilon^{(2)}_1,\ldots,\epsilon^{(2)}_N)$
are two stationary stochastic processes, we define the \emph{cross-variable spatial synchrony}
(or, simply, the \emph{cross synchrony}) between $\epsilon^{(1)}$ and $\epsilon^{(2)}$ as
\begin{equation}
\rho_{\epsilon^{(1)} \epsilon^{(2)}} = \left( \frac{1}{N^2-N} \right) \sum_{i \neq j} S_{\epsilon^{(1)}_i \epsilon^{(2)}_j}.
\end{equation}
This is a complex-valued function of frequency or timescale. Why is this interpretable as cross-variable 
spatial synchrony? A quantity representing spatial synchrony should compare values of the processes 
$\epsilon^{(1)}$ and $\epsilon^{(2)}$ in one location to values in another location, since spatial synchrony
is about relationships between distinct locations; hence our sum is over $i \neq j$. 
A quantity representing cross-variable synchrony should 
make comparisons between two variables, as opposed to comparisons between the same variable in different locations;
hence we use the cross spectrum between variable $1$ in location $i$ ($\epsilon^{(1)}_i$) and variable 
$2$ in location $j$ ($\epsilon^{(2)}_j$). 
Finally, a quantity representing cross-variable synchrony needs to
include the possibility of time delays in the relationship between the two variables. For instance, 
if $\epsilon^{(2)}_j$ is a time-lagged version of $\epsilon^{(1)}_i$, but the effects of 
$\epsilon^{(2)}_j$ on a biotic process $w_j$ are immediate, whereas the effects of $\epsilon^{(1)}_i$
on $w_i$ are delayed by the same lag, then the effects of $\epsilon^{(1)}_i$ on $w_i$ will be correlated
with the effects of $\epsilon^{(2)}_j$ on $w_j$, i.e., this combination of properties of $\epsilon^{(1)}$
and $\epsilon^{(2)}$ will produce synchrony, in the classic sense of correlation, between the biotic
process $w_i$ and $w_j$.
Thus we use the cross spectrum, $S_{\epsilon^{(1)}_i \epsilon^{(2)}_j}$, for which the phase angle at 
frequency $f$ measures the time delay between frequency-$f$ oscillations of $\epsilon^{(1)}_i$ and 
frequency-$f$ oscillations of $\epsilon^{(2)}_j$. The following examples should help clarify these features of
the definition of cross synchrony.

@@

The population model is specified starting with the equation
\begin{align}
w_i(t) &= b_1 w_i(t-1)+ \cdots + b_n w_i(t-n) \label{main_model_1} \\ 
&+ p_0^{(1)} \epsilon_i^{(1)}(t)+ \cdots + p_{m_1}^{(1)} \epsilon_i^{(1)}(t-m_1) \label{main_model_2} \\
&+ p_0^{(2)} \epsilon_i^{(2)}(t)+ \cdots + p_{m_2}^{(2)} \epsilon_i^{(2)}(t-m_2) \label{main_model_3} \\
&+ \delta_i(t), \label{main_model_4}
\end{align}
where $i=1,\ldots,N$ indexes habitat patches or sampling locations, $w_i(t)$ is a measure of the 
population in location $i$ at time $t$, and $\epsilon^{(1)}=(\epsilon_1^{(1)},\ldots,\epsilon_N^{(1)})$,
$\epsilon^{(2)}=(\epsilon_1^{(2)},\ldots,\epsilon_N^{(2)})$ and $\delta=(\delta_1,\ldots,\delta_N)$ are
environmental processes influencing the populations. Note that this model assumes from the outset 
a homogeneous influence of the environmental variables on the populations in the different
sampling locations, i.e., the parameters $p$ are spatially homogeneous. We also assume that the 
combined process $(\epsilon_1^{(1)},\ldots,\epsilon_N^{(1)},\epsilon_1^{(2)},\ldots,\epsilon_N^{(2)},\delta_1,\ldots,\delta_N)$ is a second-order stationary stochastic process (REF)
%***DAN: REFS here to Brillinger
with the expected values of its component processes equal to $0$. Finally, we assume the complex roots of the
polynomial $1-b_1 z - \cdots - b_n z^n = 0$ have modulus greater than $1$, an assumption needed for invertability of
the filter $\mcB$ which we will define below. See REF
%***DAN: add refs to Brilliger, Shumway and Stoffer, Rinsel
for background on the statistical theory of stationary stochastic processes.

Letting $I_N$ denote the $N \times N$ identity matrix, we define the linear filters 
\begin{align}
\mcP^{(1)} &= p_0^{(1)} I_N + p_1^{(1)} I_N B + \cdots + p_{m_1}^{(1)} I_N B^{m_1}, \\
\mcP^{(2)} &= p_0^{(2)} I_N + p_1^{(2)} I_N B + \cdots + p_{m_2}^{(2)} I_N B^{m_2}, \\
\mcB &= I_N - b_1 I_N B - b_2 I_N B^2 - \cdots b_n I_N B^n. \\
\end{align}
Using the language of filters and stochastic processes, the original model 
(\ref{main_model_1}-\ref{main_model_4}) can then be written as
\begin{equation}
\mcB w = \mcP^{(1)} \epsilon^{(1)} +\mcP^{(2)} \epsilon^{(2)} +\delta.\label{main_model_stochproc}
\end{equation}
Writing the model in the language of stochastic processes and linear filters makes it straightforward
to calculate the spectral matrix, $S_{ww}$, of the stochastic process, $w$, which we do in section \ref{sect:derivation}.

@@

Now, averaging the off-diagonal entries of both sides of (\ref{Sww_T1}-\ref{Sww_T6}) gives
\begin{align}
\left(\frac{1}{N^2-N}\right) \sum_{i \neq j} S_{w_i w_j} &= 
\frac{|f_{\mcP^{(1)}}|^2}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right) \sum_{i \neq j} S_{\epsilon_i^{(1)} \epsilon_j^{(1)}} \\
 &+ \frac{|f_{\mcP^{(2)}}|^2}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right) \sum_{i \neq j} S_{\epsilon_i^{(2)} \epsilon_j^{(2)}} \\
 &+ \frac{1}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right) \sum_{i \neq j} S_{\delta_i \delta_j} \\
 &+ \frac{2}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right) \sum_{i \neq j} 
  \Rp \left( f_{\mcP^{(1)}} \conj{f_{\mcP^{(2)}}} S_{\epsilon_i^{(1)} \epsilon_j^{(2)}} \right) \label{SumSww_T4}\\
 &+ \frac{2}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right)  \sum_{i \neq j} \Rp \left( f_{\mcP^{(1)}}  
 S_{\epsilon_i^{(1)} \delta_j}\right)  \label{SumSww_T5}\\
 &+ \frac{2}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right) \sum_{i \neq j} \Rp \left( f_{\mcP^{(2)}}    
 S_{\epsilon_i^{(2)} \delta_j}\right), \label{SumSww_T6}
\end{align}
\noindent where $\Rp(\cdot)$ denotes the real part, and where (\ref{SumSww_T4}-\ref{SumSww_T6})
follows from two observations: that the two summands in the brackets of each of the terms 
(\ref{Sww_T4}-\ref{Sww_T6}) are conjugate-transpose pairs; and that, for any complex matrix, $A$,
$\sum_{i \neq j} (A_{ij} +\conj{A_{ji}}) = \sum_{i \neq j} (A_{ij} +\conj{A_{ij}}) = 2 \sum_{i \neq j} \Rp (A_{ij})$.
Now, making use of the definitions of section \ref{Sect:measuring_sync}, this becomes
\begin{align}
\rho_{ww} &= \frac{|f_{\mcP^{(1)}}|^2}{|f_{\mcB}|^2} \rho_{\epsilon^{(1)} \epsilon^{(1)}}
+ \frac{|f_{\mcP^{(2)}}|^2}{|f_{\mcB}|^2} \rho_{\epsilon^{(2)} \epsilon^{(2)}}
+ \frac{1}{|f_{\mcB}|^2} \rho_{\delta \delta} \\
&+ \frac{2}{|f_{\mcB}|^2} \Rp \left(f_{\mcP^{(1)}} \conj{f_{\mcP^{(2)}}} \rho_{\epsilon^{(1)} \epsilon^{(2)}} \right) \\
&+ \frac{2}{|f_{\mcB}|^2} \Rp \left( f_{\mcP^{(1)}} \rho_{\epsilon^{(1)} \delta} \right) \\
&+ \frac{2}{|f_{\mcB}|^2} \Rp \left( f_{\mcP^{(2)}} \rho_{\epsilon^{(2)} \delta} \right).
\end{align}
If the processes $\epsilon^{(1)}$ and $\epsilon^{(2)}$ were measured and the process $\delta$ represents
the aggregate effects of unknown processes, then we can write
\begin{align}
\rho_{ww} &= \frac{|f_{\mcP^{(1)}}|^2}{|f_{\mcB}|^2} \rho_{\epsilon^{(1)} \epsilon^{(1)}} \label{rhoww_T1}\\
&+ \frac{|f_{\mcP^{(2)}}|^2}{|f_{\mcB}|^2} \rho_{\epsilon^{(2)} \epsilon^{(2)}} \label{rhoww_T2}\\
&+ \frac{2}{|f_{\mcB}|^2} \Rp \left(f_{\mcP^{(1)}} \conj{f_{\mcP^{(2)}}} \rho_{\epsilon^{(1)} \epsilon^{(2)}} \right) \label{rhoww_Tint} \\
&+ \text{other contributions}.
\end{align}
The term (\ref{rhoww_T1}) is contributions to the synchrony of $w$ due to direct Moran effects of $\epsilon^{(1)}$.
The term (\ref{rhoww_T2}) is contributions to the synchrony of $w$ due to direct Moran effects of $\epsilon^{(2)}$.
The term (\ref{rhoww_Tint}) is contributions to the synchrony of $w$ due to interactions between the Moran effects
of $\epsilon^{(1)}$ and $\epsilon^{(2)}$. The ``other contributions'' may include direct Moran effects of other,
unmeasured environmental factors, as well as interactions between these effects and Moran effects of the 
measured factors $\epsilon^{(1)}$ and $\epsilon^{(2)}$.

>>>>

If $w=(w_1,\ldots,w_N)$ is an $N$-dimensional stationary stochastic process, where the index $i=1,\ldots,N$ corresponds
to sampling locations, then we measure the synchrony of $w$ as 
\begin{equation}
\rho_{ww} = \left( \frac{1}{N^2-N}  \right) \sum_{i \neq j} S_{w_i w_j},
\end{equation}
where $S_{ww}$ is the spectral matrix of the process $w$. This is a function of frequency or timescale because
$S_{w_i w_j}$ is a function of frequency or timescale.
To see that $\rho_{ww}$ is a real-valued function, note that $\conj{S_{ww}}=S_{ww}^\tau$, where the superscript 
$\tau$ denotes matrix transpose (REF to Brillinger theorem 2.5.1 on p. 24).
%***DAN: Don't forget to fill in this reference!
Therefore 
\begin{align}
\conj{\rho_{ww}} &= \left( \frac{1}{N^2-N}  \right) \sum_{i \neq j} \conj{S_{w_i w_j}} \\
&= \left( \frac{1}{N^2-N}  \right) \sum_{i \neq j} S_{w_j w_i} \\
&= \left( \frac{1}{N^2-N}  \right) \sum_{i \neq j} S_{w_i w_j} \\
&= \rho_{ww}.
\end{align} 
The quantity $\rho_{ww}$ makes sense as a measure of synchrony in part because 
\begin{align}
\rho_{ww} &= \Rp(\rho_{ww}) \\
&= \left( \frac{1}{N^2-N} \right) \sum_{i \neq j} \Rp(S_{w_i w_j}).
\end{align}
The quantity $\Rp(S_{w_i w_j})$ is the cospectrum of the component processes $w_i$ and $w_j$, 
and an appropriate integral across frequencies of the cospectrum equals the covariance, 
$\cov(w_i,w_j)$ (REF to some specific page/theorem in Brillinger). 
%***DAN: Don't forget to add
Thus an integral of $\rho_{ww}$ across frequencies equals 
\begin{equation}
\left( \frac{1}{N^2-N} \right) \sum_{i \neq j} \cov(w_i,w_j),
\end{equation}
which is a standard quantity that can be used to measure non-frequency-specific synchrony.
Thus $\rho_{ww}$ is a frequency-specific generalization of a classic, non-frequency-specific 
measure of synchrony.

If $\epsilon^{(1)}=(\epsilon^{(1)}_1,\ldots,\epsilon^{(1)}_N)$ and 
$\epsilon^{(2)}=(\epsilon^{(2)}_1,\ldots,\epsilon^{(2)}_N)$
are two $N$-dimensional stationary stochastic processes, we define the \emph{cross-variable spatial synchrony}
(or, simply, the \emph{cross synchrony}) between $\epsilon^{(1)}$ and $\epsilon^{(2)}$ as
\begin{equation}
\rho_{\epsilon^{(1)} \epsilon^{(2)}} = \left( \frac{1}{N^2-N} \right) \sum_{i \neq j} S_{\epsilon^{(1)}_i \epsilon^{(2)}_j}.
\end{equation}
This is a complex-valued function of frequency or timescale. Why is this interpretable as cross-variable 
spatial synchrony? A quantity representing spatial synchrony should compare values of the processes 
$\epsilon^{(1)}$ and $\epsilon^{(2)}$ in one location to values in another location, since spatial synchrony
is about relationships between distinct locations; hence our sum is over $i \neq j$. 
A quantity representing cross-variable synchrony should 
make comparisons between two variables, as opposed to comparisons between the same variable in different locations;
hence we use the cross spectrum between variable $1$ in location $i$ ($\epsilon^{(1)}_i$) and variable 
$2$ in location $j$ ($\epsilon^{(2)}_j$). 
Finally, a quantity representing cross-variable synchrony needs to
include the possibility of time delays in the relationship between the two variables. For instance, 
if $\epsilon^{(2)}_j$ is a time-lagged version of $\epsilon^{(1)}_i$, but the effects of 
$\epsilon^{(2)}_j$ on a biotic process $w_j$ are immediate, whereas the effects of $\epsilon^{(1)}_i$
on $w_i$ are delayed by the same lag, then the effects of $\epsilon^{(1)}_i$ on $w_i$ will be correlated
with the effects of $\epsilon^{(2)}_j$ on $w_j$, i.e., this combination of properties of $\epsilon^{(1)}$
and $\epsilon^{(2)}$ will produce synchrony, in the classic sense of correlation, between the biotic
processes $w_i$ and $w_j$.
Thus we use the cross spectrum, $S_{\epsilon^{(1)}_i \epsilon^{(2)}_j}$, for which the phase angle at 
frequency $f$ measures the time delay between frequency-$f$ oscillations of $\epsilon^{(1)}_i$ and 
frequency-$f$ oscillations of $\epsilon^{(2)}_j$. The following examples should help clarify these features of
the definition of cross synchrony.

@@

The population model is specified starting with the equation
\begin{align}
w_i(t) &= b_1 w_i(t-1)+ \cdots + b_n w_i(t-n) \label{main_model_1} \\ 
&+ p_0^{(1)} \epsilon_i^{(1)}(t)+ \cdots + p_{m_1}^{(1)} \epsilon_i^{(1)}(t-m_1) \label{main_model_2} \\
&+ p_0^{(2)} \epsilon_i^{(2)}(t)+ \cdots + p_{m_2}^{(2)} \epsilon_i^{(2)}(t-m_2) \label{main_model_3} \\
&+ \delta_i(t), \label{main_model_4}
\end{align}
where $i=1,\ldots,N$ indexes habitat patches or sampling locations, $w_i(t)$ is a measure of the 
population in location $i$ at time $t$, and $\epsilon^{(1)}=(\epsilon_1^{(1)},\ldots,\epsilon_N^{(1)})$,
$\epsilon^{(2)}=(\epsilon_1^{(2)},\ldots,\epsilon_N^{(2)})$ and $\delta=(\delta_1,\ldots,\delta_N)$ are
environmental processes influencing the populations. Note that this model assumes from the outset 
a homogeneous influence of the environmental variables on the populations in the different
sampling locations, i.e., the parameters $p$ are spatially homogeneous. 
%We also assume spatial homogeneity of the AR coefficients, need to add a mention of that
We also assume that the 
combined process $(\epsilon_1^{(1)},\ldots,\epsilon_N^{(1)},\epsilon_1^{(2)},\ldots,\epsilon_N^{(2)},\delta_1,\ldots,\delta_N)$ is a second-order stationary stochastic process (REF)
%***DAN: REFS here to Brillinger
with the expected values of its component processes equal to $0$. Finally, we assume the complex roots of the
polynomial $1-b_1 z - \cdots - b_n z^n = 0$ have modulus greater than $1$, an assumption needed for the 
existence of a stationary stochastic process solution for the model and for invertability of
the filter $\mcB$ which we will define below. See REF
%***DAN: add refs to Brilliger, Shumway and Stoffer, Rinsel
for background on the statistical theory of stationary stochastic processes.

Letting $I_N$ denote the $N \times N$ identity matrix and letting $B$ denote the backshift operator, 
we define the linear filters 
\begin{align}
\mcP^{(1)} &= p_0^{(1)} I_N + p_1^{(1)} I_N B + \cdots + p_{m_1}^{(1)} I_N B^{m_1}, \\
\mcP^{(2)} &= p_0^{(2)} I_N + p_1^{(2)} I_N B + \cdots + p_{m_2}^{(2)} I_N B^{m_2}, \\
\mcB &= I_N - b_1 I_N B - b_2 I_N B^2 - \cdots b_n I_N B^n.
\end{align}
Using the language of filters and stochastic processes, the original model 
(\ref{main_model_1}-\ref{main_model_4}) can then be written as
\begin{equation}
\mcB w = \mcP^{(1)} \epsilon^{(1)} +\mcP^{(2)} \epsilon^{(2)} +\delta.\label{main_model_stochproc}
\end{equation}
Writing the model in the language of stochastic processes and linear filters makes it straightforward
to calculate the spectral matrix, $S_{ww}$, of the stochastic process, $w$, which we do in section \ref{sect:derivation}.

@@

Now, averaging the off-diagonal entries of both sides of (\ref{Sww_T1}-\ref{Sww_T6}) gives
\begin{align}
\left(\frac{1}{N^2-N}\right) \sum_{i \neq j} S_{w_i w_j} &= 
\frac{|f_{\mcP^{(1)}}|^2}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right) \sum_{i \neq j} S_{\epsilon_i^{(1)} \epsilon_j^{(1)}} \\
 &+ \frac{|f_{\mcP^{(2)}}|^2}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right) \sum_{i \neq j} S_{\epsilon_i^{(2)} \epsilon_j^{(2)}} \\
 &+ \frac{1}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right) \sum_{i \neq j} S_{\delta_i \delta_j} \\
 &+ \frac{2}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right) \sum_{i \neq j} 
  \Rp \left( f_{\mcP^{(1)}} \conj{f_{\mcP^{(2)}}} S_{\epsilon_i^{(1)} \epsilon_j^{(2)}} \right) \label{SumSww_T4}\\
 &+ \frac{2}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right)  \sum_{i \neq j} \Rp \left( f_{\mcP^{(1)}}  
 S_{\epsilon_i^{(1)} \delta_j}\right)  \label{SumSww_T5}\\
 &+ \frac{2}{|f_{\mcB}|^2} \left(\frac{1}{N^2-N}\right) \sum_{i \neq j} \Rp \left( f_{\mcP^{(2)}}    
 S_{\epsilon_i^{(2)} \delta_j}\right), \label{SumSww_T6}
\end{align}
\noindent where $\Rp(\cdot)$ denotes the real part, and where (\ref{SumSww_T4}-\ref{SumSww_T6})
follows from two observations: that the two summands in the brackets of each of the terms 
(\ref{Sww_T4}-\ref{Sww_T6}) are conjugate-transpose pairs; and that, for any complex matrix, $A$,
$\sum_{i \neq j} (A_{ij} +\conj{A_{ji}}) = \sum_{i \neq j} (A_{ij} +\conj{A_{ij}}) = 2 \sum_{i \neq j} \Rp (A_{ij})$.
Now, making use of the definitions of section \ref{Sect:measuring_sync}, this becomes
\begin{align}
\rho_{ww} &= \frac{|f_{\mcP^{(1)}}|^2}{|f_{\mcB}|^2} \rho_{\epsilon^{(1)} \epsilon^{(1)}}
+ \frac{|f_{\mcP^{(2)}}|^2}{|f_{\mcB}|^2} \rho_{\epsilon^{(2)} \epsilon^{(2)}}
+ \frac{1}{|f_{\mcB}|^2} \rho_{\delta \delta} \\
&+ \frac{2}{|f_{\mcB}|^2} \Rp \left(f_{\mcP^{(1)}} \conj{f_{\mcP^{(2)}}} \rho_{\epsilon^{(1)} \epsilon^{(2)}} \right) \\
&+ \frac{2}{|f_{\mcB}|^2} \Rp \left( f_{\mcP^{(1)}} \rho_{\epsilon^{(1)} \delta} \right) \\
&+ \frac{2}{|f_{\mcB}|^2} \Rp \left( f_{\mcP^{(2)}} \rho_{\epsilon^{(2)} \delta} \right),
\end{align}
which expresses population synchrony in terms of noise synchrony and cross synchrony.
If the processes $\epsilon^{(1)}$ and $\epsilon^{(2)}$ were measured and the process $\delta$ represents
the aggregate effects of unknown processes, then we can write
\begin{align}
\rho_{ww} &= \frac{|f_{\mcP^{(1)}}|^2}{|f_{\mcB}|^2} \rho_{\epsilon^{(1)} \epsilon^{(1)}} \label{rhoww_T1}\\
&+ \frac{|f_{\mcP^{(2)}}|^2}{|f_{\mcB}|^2} \rho_{\epsilon^{(2)} \epsilon^{(2)}} \label{rhoww_T2}\\
&+ \frac{2}{|f_{\mcB}|^2} \Rp \left(f_{\mcP^{(1)}} \conj{f_{\mcP^{(2)}}} \rho_{\epsilon^{(1)} \epsilon^{(2)}} \right) \label{rhoww_Tint} \\
&+ \text{other contributions}.
\end{align}
The term (\ref{rhoww_T1}) is contributions to the synchrony of $w$ due to direct Moran effects of $\epsilon^{(1)}$.
The term (\ref{rhoww_T2}) is contributions to the synchrony of $w$ due to direct Moran effects of $\epsilon^{(2)}$.
The term (\ref{rhoww_Tint}) is contributions to the synchrony of $w$ due to interactions between the Moran effects
of $\epsilon^{(1)}$ and $\epsilon^{(2)}$. The ``other contributions'' may include direct Moran effects of other,
unmeasured environmental factors, as well as interactions between these effects and Moran effects of the 
measured factors $\epsilon^{(1)}$ and $\epsilon^{(2)}$.

\section{Details of data and data cleaning}

%***DAN: This should include specification of the regions CC1, CC2, SB.
%You have to get some info from Tom about the nature of the spatial sampling, and the process leading up to what he gave me.
%You have to then describe the stages of cleaning I did.

\section{Correlation analyses to help select autoregressive model lags}

%***DAN: Describe the surrogating process
%Probably you only need to include the results in allcorfsgtd_RE, in the Results section. 
%See line 480 and above in AnalysisStep_LinearModels.R
